---
title: "GB04_Dataanalysis"
author: "Aaron Fehr"
date: "2023-06-28"
output: html_document
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(data.table)
library(protti)
library(ComplexUpset)
library(broom)
library(reshape2)
library(clusterProfiler)
library(factoextra)
library(cluster)
library(RColorBrewer)
library(ggvenn)
library(dtwclust)
library(STRINGdb)
library(factoextra)
library(foreach)
library(doParallel)
library(e1071)

organism = "org.Hs.eg.db"


library(org.Hs.eg.db)

```
Read in preprocessed data
```{r}
sw_adj = fread("./Temporal_LiP/GB02_Preprocessed_data/230727_1441_GB02_TempLiP_MSstatsAdj_DifferentialAbundance.csv")

gls_adj_raw = fread("./Temporal_LiP/GB02_Preprocessed_data/230727_1441_GB02_TempLiP_GLS_AdjustedAbundance.csv")

pep_metadata = fread("./Temporal_LiP/GB02_Preprocessed_data/230727_1441_GB02_TempLiPLiP_Peptide_Metadata.csv")

uniprot = fread("Uniprot_human_230420.tsv")
```
Data wrangling and make time series data frame
```{r}
gls_adj = gls_adj_raw %>%
  mutate(time = gsub("-0_min","",contrast)) %>%
  left_join(pep_metadata %>%
              dplyr::select(Gene, pg_protein_accessions, eg_modified_sequence) %>%
              unique(),
            by = "eg_modified_sequence")


gls_time = rbind(
  gls_adj %>%
    dplyr::select(Gene,
                  pg_protein_accessions,
                  eg_modified_sequence,
                  time,
                  estimate,
                  adj_pval),
  gls_adj %>%
    dplyr::select(Gene,
                  pg_protein_accessions,
                  eg_modified_sequence,
                  time,
                  estimate,
                  adj_pval) %>%
    mutate(time = "0_min",
           estimate = 0,
           adj_pval = 1) %>%
    unique()) %>%
  group_by(eg_modified_sequence) %>%
  mutate(mean_est = mean(estimate)) %>%
  mutate(estimate = case_when(
    mean_est < 0 ~ - estimate,
    mean_est >= 0 ~ estimate
  )) %>%
  dplyr::select(-mean_est) %>%  
  mutate(time_num = as.numeric(gsub("_min","",time))) %>%
  mutate(max_est = max(abs(estimate))) %>%
  mutate(min_adj_pval = min(adj_pval)) %>%
  mutate(sig = adj_pval <= 0.05 & abs(estimate) >= 1) %>%
  mutate(n_sig = sum(sig)) %>%
  mutate(zscore = scale(estimate, center = TRUE, scale = TRUE)) %>%
  mutate(max_min_score = (estimate - min(estimate))/(max(estimate)-min(estimate))) %>%
  arrange(eg_modified_sequence, time_num) %>%
  mutate(adjecent_sig = max(sig) * (max(cumsum(sig * lag(sig, default = 0))) +1)) %>%
  ungroup() %>%
  group_by(pg_protein_accessions, time) %>%
  mutate(n_sig_per_prot = sum(sig)) %>%
  mutate(n_tot = n()) %>%
  mutate(rel_sig_per_prot = n_sig_per_prot/n_tot) %>%
  ungroup()



# make wider data frame and filter for significance and >= 2 peptides/protein

gls_time_wide = gls_time %>%
  dplyr::filter(n_tot > 1) %>%
  dplyr::filter(n_sig > 1) %>%
  pivot_wider(id_cols = c("Gene","pg_protein_accessions", "eg_modified_sequence","adjecent_sig"), values_from = c("max_min_score"), names_from = "time") 

```

Plot of number of changes
```{r}
# Changes per time point and protein 

relative_changes_plot = gls_time %>%
  dplyr::filter(time_num != 0) %>%
  dplyr::filter(n_sig_per_prot > 0) %>%
  dplyr::select(time_num, rel_sig_per_prot) %>%
  unique() %>%
  ggplot(aes(rel_sig_per_prot)) +
  theme_classic() +
  scale_fill_brewer(palette = "BuPu") +
  geom_histogram(color = "black", bins = 25, fill = "lightgrey") +
  labs(title = " ", x = "Relative LiP changes per protein", y = "Number of peptides per bin") +
  facet_wrap(. ~ as.factor(time_num))


relative_changes_plot



ggsave("./Temporal_LiP/GB02_AnalysisOutput/GB02_plots/Relative_Changes.png",
       relative_changes_plot,
       height = 4,
       width = 7)


```

Comparison with SW correction
```{r}
test = gls_adj %>%
  inner_join(sw_adj %>%
               mutate(time = paste0(time, "_min")), by = c("eg_modified_sequence","time"))


Cor = cor(test$estimate, test$adj_diff)


plot = test %>%
  mutate(facet = paste0("Correlation of Log2FC: ",Cor)) %>%
  ggplot(aes(estimate, adj_diff)) +
  geom_point()+
  theme_bw() +
  theme(strip.background = element_blank()) +
  labs(title = "", x = "GLS", y = "MSstasts") +
  facet_wrap(.~ facet)


ggsave("./Temporal_LiP/GB02_AnalysisOutput/GB02_plots/MSstats_log2fc.png",
       plot,
       height = 3,
       width = 5)


plot

Cor = cor(test$p.value, test$pval)


plot = test %>%
  mutate(facet = paste0("Correlation of p-values: ", round(Cor,2))) %>%
  ggplot(aes(p.value, pval)) +
  geom_point(alpha = .01)+
  theme_bw() +
  theme(strip.background = element_blank()) +
  geom_density2d(color = "orange") +
  labs(title = "", x = "GLS", y = "MSstasts") +
  facet_wrap(.~ facet)

ggsave("./Temporal_LiP/GB02_AnalysisOutput/GB02_plots/MSstats_pval.png",
       plot,
       height = 3,
       width = 5)

plot

```

Hierarchical Clustering

```{r}
set.seed(1234)
# Parameters to test:

k_clusters = 15

# Make cluster data
cluster_data_lip = gls_time_wide[5:ncol(gls_time_wide)]

# calculate distance matrix and clusters

dist = dist(cluster_data_lip) 

hc_lip = hclust(dist, method = "average")

clusters = cutree(hc_lip, k = k_clusters)

# Combine with original data

lip_hc_clustered = cbind(gls_time_wide, clusters) %>%
  as.data.frame() %>%
  dplyr::select(eg_modified_sequence, clusters) %>%
  left_join(gls_time) %>%
  group_by(clusters, time) %>%
  mutate(obs_per_cluster = n()) %>%
  mutate(est_centroid = mean(estimate)) %>%
  mutate(zscore_centroid = mean(zscore)) %>%
  mutate(maxmin_centroid = mean(max_min_score)) %>%
  ungroup()


# Plotting of Dendrogram

plot(hc_lip, main = "Hierarchical clustering of LiP data:",xlab = "", ylab = "", pch = clusters, labels = F)
rect.hclust(hc_lip, k = k_clusters, cluster = clusters, border = 1:k_clusters)


svg("./Temporal_LiP/GB02_AnalysisOutput/GB02_plots/Dendrogram.svg")

# Code of the plot
plot(hc_lip, main = "Hierarchical clustering of LiP data:",xlab = "", ylab = "", pch = clusters, labels = F)
rect.hclust(hc_lip, k = k_clusters, cluster = clusters, border = 1:k_clusters)

dev.off() 


# PCA + Clusters


fviz_cluster(list(data = cluster_data_lip, cluster = clusters))
```




Peptide trace plots: 
```{r}
# All time series:

plot = rbind(lip_hc_clustered %>%
  dplyr::select(time_num, eg_modified_sequence, clusters, FC = max_min_score, Centroid = maxmin_centroid) %>%
  mutate(Norm = "Max-Min-FC"),
  lip_hc_clustered %>%
  dplyr::select(time_num, eg_modified_sequence, clusters, FC = estimate, Centroid = est_centroid) %>%
  mutate(Norm = "Log2-FC")) %>%
  mutate(clusters = paste0("Cluster ",clusters)) %>%
  ggplot(aes(x = time_num, y = FC, group = eg_modified_sequence)) +
  geom_line(alpha = 0.2)+
  geom_line(aes(x = time_num, y = Centroid, color = "red")) +
  geom_point(aes(x = time_num, y = Centroid, color = "red")) +
  theme_bw()+
  theme(strip.background = element_blank()) +
  theme(axis.text.x = element_text(hjust = 1, angle = 45)) +
  facet_grid(Norm ~ clusters,  scales = "free_y")+
  labs(title = " ", x = "", y = "")+
  guides(color="none")

plot


ggsave("./Temporal_LiP/GB02_AnalysisOutput/GB02_plots/All_ts_cluster_plot.png",
       plot,
       height = 3,
       width = 10)

# Selected clusters (over 10 peptides)


plot = rbind(lip_hc_clustered %>%
  dplyr::filter(obs_per_cluster >= 10) %>%
  dplyr::select(time_num, eg_modified_sequence, clusters, FC = max_min_score, Centroid = maxmin_centroid) %>%
  mutate(Norm = "Max-Min-FC"),
  lip_hc_clustered %>%
  dplyr::filter(obs_per_cluster >= 10) %>%
  dplyr::select(time_num, eg_modified_sequence, clusters, FC = estimate, Centroid = est_centroid) %>%
  mutate(Norm = "Log2-FC")) %>%
  mutate(clusters = paste0("Cluster ",clusters)) %>%
  ggplot(aes(x = time_num, y = FC, group = eg_modified_sequence)) +
  geom_line(alpha = 0.2)+
  geom_line(aes(x = time_num, y = Centroid, color = "red")) +
  geom_point(aes(x = time_num, y = Centroid, color = "red")) +
  theme_bw()+
  theme(strip.background = element_blank()) +
  facet_grid(Norm ~ clusters,  scales = "free_y")+
  labs(title = " ", x = "", y = "")+
  guides(color="none")
  
plot


ggsave("./Temporal_LiP/GB02_AnalysisOutput/GB02_plots/Selected_ts_cluster_plot.png",
       plot,
       height = 3,
       width = 10)



```



Call proteins based on cluster abundance

```{r}
# Call proteins based on cluster annotation -> majority vote
# If same number of peptides from multiple clusters -> in multiple clusters

hc_call = lip_hc_clustered  %>%
  group_by(clusters, time) %>%
  unique() %>%
  dplyr::select(Gene, eg_modified_sequence, pg_protein_accessions, clusters) %>%
  unique() %>%
  group_by(pg_protein_accessions) %>%
  mutate(n_pep = n()/5) %>%
  group_by(pg_protein_accessions, clusters) %>%
  mutate(n_per_cluster = n()/5) %>%
  group_by(pg_protein_accessions) %>%
  mutate(rel = n_per_cluster/n_pep) %>%
  mutate(max_rel = max(rel)) %>%
  ungroup() %>%
  dplyr::filter(rel == max_rel) %>% 
  dplyr::select(Gene, pg_protein_accessions, clusters, max_rel, n_pep) %>%
  unique() %>%
  group_by(clusters) %>%
  mutate(prot_per_cluster = n()) %>%
  ungroup()

hc_call %>%
  group_by(Gene) %>%
  mutate(N = n()) %>%
  ungroup() %>%
  dplyr::select(N) %>%
  group_by(N) %>%
  mutate(Number_n = n()) %>%
  unique()

lip_hc_clustered %>%
  dplyr::select(clusters, Gene) %>%
  unique() %>%
  group_by(Gene) %>%
  mutate(N = n()) %>%
  ungroup() %>%
  dplyr::select(N) %>%
  group_by(N) %>%
  mutate(Number_n = n()) %>%
  unique()

```



Plot with significant pep/prot per time point and features per cluster
```{r}
# Significant changes per time point:

sig_per_time = rbind(
  gls_time %>%
    dplyr::select(pg_protein_accessions, x_value = time_num, sig) %>%
    group_by(x_value, pg_protein_accessions) %>%
    mutate(sig_prot = sum(sig) > 0) %>%
    dplyr::select(sig_prot) %>%
    unique()  %>%
    group_by(x_value) %>%
    mutate(value = sum(sig_prot)/n()*100) %>%
    dplyr::select(value) %>%
    mutate(entity = "Protein") %>%
    unique(),
  gls_time %>%
    dplyr::select(eg_modified_sequence, x_value = time_num, sig) %>%
    group_by(x_value) %>%
    mutate(value = sum(sig)/n()*100) %>%
    dplyr::select(value) %>%
    unique()  %>%
    mutate(entity = "Peptide")) %>%
  dplyr::filter(x_value != 0) %>%
  arrange(x_value) %>%
  ungroup() %>%
  mutate(order = row_number()) %>%
  mutate(x_value = as.character(x_value)) %>%
  mutate(facet = "% Significant/time point")


plot = sig_per_time %>%
  mutate(x_value = fct_reorder(x_value, order)) %>%
  ggplot(aes(x = x_value, y = value, fill = entity)) +
  geom_col(position = position_dodge(), color = "black")+
  theme_bw()+ 
  theme(legend.position = "left",
        legend.key.size = unit(0.4, "cm"),
        legend.margin = margin(r=- 0.6, unit = "cm")) + 
  theme(panel.grid = element_blank()) +
  theme(strip.background = element_blank()) +
  scale_fill_brewer(palette = "BuPu") +
  labs(title = " ",x = "", y = "", fill = "")+
  facet_wrap(. ~ facet, scales = "free")
  
plot

ggsave(paste0("./Temporal_LiP/GB02_AnalysisOutput/GB02_plots/Relative_Sig_per_timepoint.png"),
      plot,
      height = 3,
      width = 3)


#Plot Features per cluster

n_per_cluster = rbind(
  lip_hc_clustered %>%
    dplyr::select(eg_modified_sequence, x_value = clusters) %>%
    unique() %>%
    group_by(x_value) %>%
    mutate(value = n()) %>%
    dplyr::select(value) %>%
    unique() %>%
    mutate(entity = "Peptide") %>%
    mutate(x_value = case_when(
       value < 10 ~ "other",
       TRUE ~ as.factor(x_value)
    )) %>%
    mutate(value = sum(value)) %>%
    unique(),  
  lip_hc_clustered %>%
    dplyr::select(pg_protein_accessions, x_value = clusters) %>%
    unique() %>%
    group_by(x_value) %>%
    mutate(value = n()) %>%
    dplyr::select(value) %>%
    unique() %>%
    mutate(entity = "Peptide") %>%
    mutate(x_value = case_when(
       value < 10 ~ "other",
       TRUE ~ as.factor(x_value))
       ) %>%
    mutate(value = sum(value)) %>%
    unique() %>%
    mutate(entity = "Protein")) %>%
  ungroup() %>%
  arrange(x_value) %>%
  mutate(order = row_number()) %>%
  mutate(facet = "Features/cluster")



plot = n_per_cluster %>%
  mutate(x_value = fct_reorder(as.factor(x_value), order)) %>%
  ggplot(aes(x = x_value, y = value, fill = entity)) +
  geom_col(position = position_dodge(), color = "black")+
  theme_bw()+ 
  theme(legend.position = "left",
        legend.key.size = unit(0.4, "cm"),
        legend.margin = margin(r=- 0.6, unit = "cm")) + 
  theme(panel.grid = element_blank()) +
  theme(strip.background = element_blank()) +
  scale_fill_brewer(palette = "BuPu") +
  labs(title = " ",x = "", y = "", fill = "")+
  facet_wrap(. ~ facet, scales = "free")
  
plot

ggsave(paste0("./Temporal_LiP/GB02_AnalysisOutput/GB02_plots/Features_per_cluster.png"),
      plot,
      height = 3,
      width = 5)



# Combined:


plot = rbind(sig_per_time, n_per_cluster) %>%
  mutate(x_value = fct_reorder(x_value, order)) %>%
  ggplot(aes(x = x_value, y = value, fill = entity)) +
  geom_col(position = position_dodge(), color = "black")+
  theme_bw()+ 
  theme(legend.position = "left",
        legend.key.size = unit(0.4, "cm"),
        legend.margin = margin(r=- 0.6, unit = "cm")) + 
  theme(panel.grid = element_blank()) +
  theme(strip.background = element_blank()) +
  scale_fill_brewer(palette = "BuPu") +
  labs(title = " ",x = "", y = "", fill = "")+
  facet_wrap(. ~ facet, scales = "free")

plot

ggsave(paste0("./Temporal_LiP/GB02_AnalysisOutput/GB02_plots/Features_per_clusterANDSigPerTP.png"),
      plot,
      height = 3,
      width = 5)


#For dendrogram title:

plot = n_per_cluster %>%
  mutate(facet = "Hierarchical clustering of peptide traces") %>%
  ggplot(aes(x = x_value, y = value, fill = entity)) +
  geom_col(position = position_dodge(), color = "black")+
  theme_bw()+ 
  theme(legend.position = "left",
        legend.key.size = unit(0.4, "cm"),
        legend.margin = margin(r=- 0.6, unit = "cm")) + 
  theme(panel.grid = element_blank()) +
  theme(strip.background = element_blank()) +
  scale_fill_brewer(palette = "BuPu") +
  labs(title = " ",x = "", y = "", fill = "")+
  facet_wrap(. ~ facet, scales = "free")

ggsave(paste0("./Temporal_LiP/GB02_AnalysisOutput/GB02_plots/DendroTitle.png"),
      plot,
      height = 3,
      width = 4)

```




GO-Enrichment of clusters
```{r}
set.seed(123)

#GO over representation analysis for clusters:

universe = unique(gls_adj$pg_protein_accessions)

cluster = unique(hc_call$clusters)


GO_overrep_Lip_BP = data.frame()

for (i in cluster){
  
  genes = (hc_call %>%
    filter(clusters == i) %>%
    dplyr::select(pg_protein_accessions) %>%
    unique())$pg_protein_accessions
  
  tryCatch({
    
      GO = enrichGO(gene = genes, 
           ont ="BP",
           keyType = "UNIPROT",
           universe = universe,
           pvalueCutoff = 1, 
           minGSSize = 5,
           maxGSSize = 500,
           OrgDb = organism, 
           pAdjustMethod = "BH")

  
      simple_GO = simplify(GO, cutoff = 0.7)

  plot = dotplot(GO, showCategory=20)+
    labs(title = paste0("GO:Biological Process LiP cluster ", i))
  
  plot_simple = dotplot(simple_GO, showCategory=20)+
    labs(title = paste0("GO:Simplified Biological Process LiP cluster ", i))
  

   ggsave(paste0("./Temporal_LiP/GB02_AnalysisOutput/GB02_plots/GO_BP_Cluster_",i,"_simplified.png"),
        plot_simple,
        height = 10,
        width = 9)
   
    ggsave(paste0("./Temporal_LiP/GB02_AnalysisOutput/GB02_plots/GO_BP_Cluster_",i,".png"),
        plot,
        height = 10,
        width = 9)
   

  GO_overrep_Lip_BP = rbind(GO_overrep_Lip_BP, as.data.frame(GO@result) %>%
    mutate(cluster = i))
  
  # print(plot)
  
  print(plot_simple)
  
  print(i)
  
  
  },
 error = function(e)
 print(paste0("No significant enrichment in cluster ",i)) 
 )
}






GO_overrep_LiP_MF = data.frame()


for (i in cluster){
  
  genes = (hc_call %>%
    filter(clusters == i) %>%
    dplyr::select(pg_protein_accessions) %>%
    unique())$pg_protein_accessions
  
  tryCatch({
  
  GO = enrichGO(gene = genes, 
           ont ="MF",
       keyType = "UNIPROT",
       universe = universe,
       pvalueCutoff = 1, 
       minGSSize = 10,
       maxGSSize = 500,
       OrgDb = organism, 
       pAdjustMethod = "BH")

  simple_GO = simplify(GO, cutoff = 0.7)
  
  plot = dotplot(GO, showCategory=20)+
    labs(title = paste0("GO:Molecular Function LiP cluster ", i))
  
  plot_simple = dotplot(simple_GO, showCategory=20)+
    labs(title = paste0("GO:Simplified Molecular Function LiP cluster ", i))
  
   ggsave(paste0("./Temporal_LiP/GB02_AnalysisOutput/GB02_plots/GO_MF_Cluster_",i,"_simplified.png"),
        plot_simple,
        height = 10,
        width = 9)
   
  ggsave(paste0("./Temporal_LiP/GB02_AnalysisOutput/GB02_plots/GO_MF_Cluster_",i,".png"),
        plot,
        height = 10,
        width = 9)
  
  GO_overrep_LiP_MF = rbind(GO_overrep_LiP_MF, as.data.frame(GO@result) %>%
    mutate(cluster = i))
  
  
  
  #print(plot)
  
  print(plot_simple)
  
    
  },
 error = function(e)
 print(paste0("No significant enrichment in cluster ",i))
  )
}
```



Plots of unfiltered top 25 GO terms for all clusters
```{r}
cluster = seq(1:k_clusters)

for (i in cluster){
  temp_BP = GO_overrep_Lip_BP %>% 
    dplyr::filter(cluster == i) %>%
    arrange(p.adjust) %>%
    mutate(rank = row_number()) %>%
    dplyr::filter(rank <= 25) %>%
    mutate(GO_type = "Biological Process") %>%
    separate(GeneRatio, into = c("n_GO","n_prot"), sep = "/") %>%
    mutate(GeneRatio = as.numeric(n_GO)/as.numeric((n_prot)))
  
  temp_MF  = GO_overrep_LiP_MF %>% 
    dplyr::filter(cluster == i) %>%
    arrange(p.adjust) %>%
    mutate(rank = row_number()) %>%
    dplyr::filter(rank <= 25) %>%
    mutate(GO_type = "Molecular Function") %>%
    separate(GeneRatio, into = c("n_GO","n_prot"), sep = "/") %>%
    mutate(GeneRatio = as.numeric(n_GO)/as.numeric((n_prot)))
  
  n_prot = unique(temp_BP$n_prot)

  if(nrow(temp_BP) > 0 & nrow(temp_MF > 0)){
    plot = rbind(temp_BP, temp_MF) %>%
      group_by(GO_type) %>%
      mutate(Description = fct_reorder(Description, GeneRatio)) %>%
      ggplot(aes(y = Description, x = GeneRatio, fill = p.adjust)) +
      theme_bw()+
      theme(panel.grid = element_blank()) +
      theme(strip.background = element_blank()) +
      scale_fill_gradient2(low = "#810f7c", mid = "#8c96c6",high = "#f7fcfd", 
                       midpoint = 0.025, breaks = c(0,0.1, 0.02, 0.03, 0.04, 0.05), 
                       limits = c(0,0.05))+
      geom_col(color = "black") + 
      labs(title = paste0("GO-Enrichments for cluster ",i, " with ", n_prot, " Proteins"), y = "", x = "Gene Ratio", fill = "adj. pvalue") +
      facet_wrap(GO_type ~., scales = "free_y")
  
    print(plot)
    
    
    ggsave(paste0("./Temporal_LiP/GB02_AnalysisOutput/GB02_plots/AllGO/SupplementaryGO_cluster",i,".png"),
    plot,
    height = 5,
    width = 20)
    
    }
  else{
    print(paste0("No significant enrichment in cluster ", i))
  }
  


}

  

```

GO: Enrichment for trends:

```{r}
set.seed(123)

#GO over representation analysis for early response clusters (1, 2, 6, 9):

genes = (hc_call %>%
           filter(clusters %in% c(1, 2, 6, 9)) %>%
           dplyr::select(pg_protein_accessions) %>%
           unique())$pg_protein_accessions
  

GO_BP_early_response = enrichGO(gene = genes, 
           ont ="BP",
           keyType = "UNIPROT",
           universe = universe,
           pvalueCutoff = 1, 
           minGSSize = 5,
           maxGSSize = 500,
           OrgDb = organism, 
           pAdjustMethod = "BH") 

GO_MF_early_response = enrichGO(gene = genes, 
           ont ="MF",
           keyType = "UNIPROT",
           universe = universe,
           pvalueCutoff = 1, 
           minGSSize = 5,
           maxGSSize = 500,
           OrgDb = organism, 
           pAdjustMethod = "BH") %>%
  mutate(GO_type = "Molecular Function")

GO_early_response = rbind(GO_BP_early_response@result %>%
                           mutate(GO_type = "Biological Process"),
                         GO_MF_early_response@result %>%
                           mutate(GO_type = "Molecular Function")) %>%
  group_by(GO_type) %>%
  arrange(p.adjust) %>%
  mutate(rank = row_number()) %>%
  separate(GeneRatio, into = c("n_GO","n_prot"), sep = "/") %>%
  mutate(GeneRatio = as.numeric(n_GO)/as.numeric((n_prot))) %>%
  mutate(Description = fct_reorder(Description, GeneRatio)) %>%
  ungroup()

  

#GO over representation analysis for late response clusters (3, 4, 5, 8)

genes = (hc_call %>%
           filter(clusters %in% c(3, 4, 5, 8)) %>%
           dplyr::select(pg_protein_accessions) %>%
           unique())$pg_protein_accessions
  

GO_BP_late_response = enrichGO(gene = genes, 
           ont ="BP",
           keyType = "UNIPROT",
           universe = universe,
           pvalueCutoff = 1, 
           minGSSize = 5,
           maxGSSize = 500,
           OrgDb = organism, 
           pAdjustMethod = "BH") %>%
  mutate(GO_type = "Biological Process") 

GO_MF_late_response = enrichGO(gene = genes, 
           ont ="MF",
           keyType = "UNIPROT",
           universe = universe,
           pvalueCutoff = 1, 
           minGSSize = 5,
           maxGSSize = 500,
           OrgDb = organism, 
           pAdjustMethod = "BH") %>%
  mutate(GO_type = "Molecular Function")


GO_late_response = rbind(GO_BP_late_response@result %>%
                           mutate(GO_type = "Biological Process"),
                         GO_MF_late_response@result %>%
                           mutate(GO_type = "Molecular Function")) %>%
  group_by(GO_type) %>%
  arrange(p.adjust) %>%
  mutate(rank = row_number()) %>%
  separate(GeneRatio, into = c("n_GO","n_prot"), sep = "/") %>%
  mutate(GeneRatio = as.numeric(n_GO)/as.numeric((n_prot))) %>%
  mutate(Description = fct_reorder(Description, GeneRatio)) %>%
  ungroup()

#CONTROL: 


genes = unique(hc_call$pg_protein_accessions)
  

GO_BP_control = enrichGO(gene = genes, 
           ont ="BP",
           keyType = "UNIPROT",
           universe = universe,
           pvalueCutoff = 1, 
           minGSSize = 5,
           maxGSSize = 500,
           OrgDb = organism, 
           pAdjustMethod = "BH") %>%
  mutate(GO_type = "Biological Process") 

GO_MF__control = enrichGO(gene = genes, 
           ont ="MF",
           keyType = "UNIPROT",
           universe = universe,
           pvalueCutoff = 1, 
           minGSSize = 5,
           maxGSSize = 500,
           OrgDb = organism, 
           pAdjustMethod = "BH") %>%
  mutate(GO_type = "Molecular Function")


GO_control = rbind(GO_BP_control@result %>%
                           mutate(GO_type = "Biological Process"),
                   GO_MF__control@result %>%
                           mutate(GO_type = "Molecular Function")) %>%
  group_by(GO_type) %>%
  arrange(p.adjust) %>%
  mutate(rank = row_number()) %>%
  separate(GeneRatio, into = c("n_GO","n_prot"), sep = "/") %>%
  mutate(GeneRatio = as.numeric(n_GO)/as.numeric((n_prot))) %>%
  mutate(Description = fct_reorder(Description, GeneRatio)) %>%
  ungroup()

```

Plotting of early and late response:
```{r}
# Top 25 early

n_prot = unique(GO_early_response$n_prot)

plot = GO_early_response %>%
  dplyr::filter(p.adjust <= 0.05) %>%
      ggplot(aes(y = Description, x = GeneRatio, fill = p.adjust)) +
      theme_bw()+
      theme(panel.grid = element_blank()) +
      theme(strip.background = element_blank()) +
      scale_fill_gradient2(low = "#810f7c", mid = "#8c96c6",high = "#f7fcfd", 
                       midpoint = 0.025, breaks = c(0,0.1, 0.02, 0.03, 0.04, 0.05), 
                       limits = c(0,0.05))+
      geom_col(color = "black") + 
      labs(title = paste0("GO-Enrichments for early response clusters (1,2,6,9) with ", n_prot, " Proteins"), y = "", x = "Gene Ratio", fill = "adj. pvalue") +
      facet_wrap(GO_type ~., scales = "free_y")
  
plot


ggsave(paste0("./Temporal_LiP/GB02_AnalysisOutput/GB02_plots/AllGO/SupplementaryGO_cluster_Early_Response.png"),
       plot,
      height = 20,
      width = 10)

# Top 25 late

n_prot = unique(GO_late_response$n_prot)

plot = GO_late_response %>%
  dplyr::filter(p.adjust <= 0.05) %>%
      ggplot(aes(y = Description, x = GeneRatio, fill = p.adjust)) +
      theme_bw()+
      theme(panel.grid = element_blank()) +
      theme(strip.background = element_blank()) +
      scale_fill_gradient2(low = "#810f7c", mid = "#8c96c6",high = "#f7fcfd", 
                       midpoint = 0.025, breaks = c(0,0.1, 0.02, 0.03, 0.04, 0.05), 
                       limits = c(0,0.05))+
      geom_col(color = "black") + 
      labs(title = paste0("GO-Enrichments for late response clusters (3,4,5,8) with ", n_prot, " Proteins"), y = "", x = "Gene Ratio", fill = "adj. pvalue") +
      facet_wrap(GO_type ~., scales = "free_y")
  
plot

ggsave(paste0("./Temporal_LiP/GB02_AnalysisOutput/GB02_plots/AllGO/SupplementaryGO_cluster_Late_Response.png"),
       plot,
      height = 20,
      width = 10)

```




GO: Reduced plot for early and late response
```{r}
BP_early = paste0("Biological Process",c(1,2,5,6,12,13,14,17,29,39,47,50,58,68))

MF_early = paste0("Molecular Function",c(1,2,3,4,7,10,11,15,22,29))

BP_late = paste0("Biological Process",c(1,6,7,8,20,22,25,27,21,30,27))

MF_late = paste0("Molecular Function",c(1,2,3,4,5,6,12,15,16,18,21))

plot = rbind(GO_early_response %>%
               mutate(selection = paste0(GO_type, rank)) %>%
               dplyr::filter(selection %in% BP_early | selection %in% MF_early) %>%
               mutate(Response = "Early response"),
             GO_late_response %>%
               mutate(selection = paste0(GO_type, rank)) %>%
               dplyr::filter(selection %in% BP_late | selection %in% MF_late) %>%
               mutate(Response = "Late response")) %>% 
  ungroup() %>%
  mutate(Description = gsub("protein tyrosine","protein\ntyrosine", Description)) %>%
  mutate(Description = gsub("protein-coupled","protein-\ncoupled", Description)) %>%
  mutate(Description = gsub("interspecies interaction","interspecies\ninteraction", Description)) %>%
  mutate(Description = fct_reorder(Description, Count)) %>%
  ggplot(aes(y = Description, x = GeneRatio, fill = p.adjust)) +
      theme_bw()+
      theme(panel.grid = element_blank()) +
      theme(strip.background = element_blank()) +
      theme(axis.text.y = element_text(lineheight = 0.75, size = 8))  +
      scale_fill_gradient2(low = "#810f7c", mid = "#8c96c6",high = "#f7fcfd", 
                       midpoint = 0.025, breaks = c(0,0.1, 0.02, 0.03, 0.04, 0.05), 
                       limits = c(0,0.05))+
      geom_col(color = "black") + 
      labs(y = "", x = "Gene Ratio", fill = "adj. pvalue") +
      facet_wrap(Response ~ GO_type, scales = "free_y")



plot
  

ggsave(paste0("./Temporal_LiP/GB02_AnalysisOutput/GB02_plots/AllGO/Main_GOfiltered_Response.png"),
       plot,
       height = 8,
       width = 10)


# Write supplementary tables:

table = GO_early_response %>%
  mutate(GeneRatio = round(GeneRatio, 3)) %>%
  dplyr::select(Description, Count, GeneRatio, p.adjust, GO_type) %>%
  arrange(p.adjust, GO_type) %>%
  dplyr::filter(p.adjust <= 0.05) 

fwrite(table, "./Temporal_LiP/GB02_AnalysisOutput/GO_early_supplementarytable.csv")


table = GO_late_response %>%
  mutate(GeneRatio = round(GeneRatio, 3)) %>%
  dplyr::select(Description, Count, GeneRatio, p.adjust, GO_type) %>%
  arrange(p.adjust, GO_type) %>%
  dplyr::filter(p.adjust <= 0.05) 

fwrite(table, "./Temporal_LiP/GB02_AnalysisOutput/GO_late_supplementarytable.csv")





```


