---
title: "GB04_LinearModel"
author: "Aaron Fehr"
date: "2023-06-27"
output: html_document
---
**Calculate differential LiP abundance:**

1.  Combine Lip and Trp data in long-format, such that there is a time, intensity and type (trp-protein intensity or lip-peptide intensity) column
2.  Filter for presence in all conditions
3.  For each peptide, fit a generalized linear model (because of unequal variances between peptides and proteins):

intensity \~ time \* (protein or peptide)

with time as factor using the estimated marginal means package and

4.  Calculate estimated marginal means
5.  Calculate differential abundance for contrasts of interest and correct for multiple comparisons using the Dunnett correction
6.  Aggregate all values of importance (coefficients = fold changes, p values, ..)
7.  Correct for multiple testing for each time point separately (Benjamini-Hochberg)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(protti)
library(broom)
library(data.table)
library(emmeans)
library(nlme)
library(foreach)
library(doParallel)
library(tictoc)
```

Read preprocessed data
```{r}
Experiment_Name = "GB02_TempLiP"
Run = format(Sys.time(), "%y%m%d_%H%M")

lip_pep = fread("./Temporal_LiP/GB02_Preprocessed_data/230717_1435_GB02_TempLiPLiP_Summarized_Peptides.csv")

trp_prot = fread("./Temporal_LiP/GB02_Preprocessed_data/230717_1435_GB02_TempLiP_Trp_Summarized_Proteins.csv")
```

Make Input dataframe
```{r}
seq_dict = lip_pep %>%
  dplyr::select(eg_modified_sequence, pg_protein_accessions) %>%
  unique()

# By using right join, only peptides with a corresponding protein measurement
# are retained
lm_raw = rbind(
  right_join(seq_dict, trp_prot %>%
    dplyr::select(sample, r_condition, pg_protein_accessions, intensity = normalised_intensity_log2) %>%
      mutate(variable = "protein") %>%
    unique(),
    by = "pg_protein_accessions"),
  lip_pep %>%
    dplyr::select(eg_modified_sequence, pg_protein_accessions, sample, r_condition, intensity = pep_int) %>%
    mutate(variable = "peptide") %>%
    unique())
    

lm_input = lm_raw %>%
  dplyr::select(r_condition, eg_modified_sequence, variable) %>%
  unique() %>%
  group_by(eg_modified_sequence) %>%
  mutate(n_timepoints = n()) %>%
  dplyr::filter(n_timepoints == 10) %>%
  ungroup() %>%
  dplyr::select(eg_modified_sequence) %>%
  unique() %>%
  left_join(lm_raw) %>%
  as.data.table()
```


Make contrast matrix:

we want to compare (Peptide - Protein) between all time points and time point 0

```{r}
levels = levels(as.factor(lm_input$r_condition))

adjustment_matrix = matrix(nrow = length(levels), ncol = 2*length(levels))
adjustment_matrix[,] = 0
rownames(adjustment_matrix) = levels

for (i in 1:length(levels)){
  adjustment_matrix[i,i] = 1
  adjustment_matrix[i,length(levels)+i] = -1
}

contrast_matrix = list()

for(i in levels[2:length(levels)]){
  
  x = paste0(i, "-0_min")
  vector = adjustment_matrix[i,] - adjustment_matrix[1,]
  contrast_matrix[x] = list(vector)
  
}

contrast_matrix
```


Run linear modelling

```{r}
set.seed(724)

# Set of peptides for model fit
peptides = unique(lm_input$eg_modified_sequence)

#Error-data to append
error_result = data.table(contrast = "none",
                          estimate = NA,
                          SE = NA,
                          df = NA,
                          t.ratio = NA,
                          p.value = NA,
                          eg_modified_sequence = character())

# Set number of cores and initialize clusters
num_cores = 3

cl = makeCluster(num_cores)
registerDoParallel(cl)

tic("Since starting the loop")

# Run parallelized foreach loop; iterating over peptides and calculating 
# gls for each peptide. If the model does not converge using restricted maximum
# likelihood, the modelling is repeated maximizing the log-likelihood. If this 
# fails as well, none is written into the method column.

gls_results = foreach(i = peptides, .combine = rbind, .packages = c("data.table","emmeans","nlme")) %dopar% {
  
  # filter data
  lm_in = lm_input[eg_modified_sequence == i]

  tryCatch({

    model = gls(intensity ~ r_condition * variable, data = lm_in, weights = varIdent(form = ~ 1 | variable))
    
    est_marginal_means = emmeans(model, specs =  ~ r_condition * variable, data = lm_in)
    
    results = as.data.table(contrast(est_marginal_means, 
                     method = contrast_matrix, 
                     adjust = "dunnettx"))[,eg_modified_sequence := i]
    
    results[,method := "REML"]
   },
   error = function(e){
     
     model = gls(intensity ~ r_condition * variable, data = lm_in, method = "ML", weights = varIdent(form = ~ 1 | variable))
     
     est_marginal_means = emmeans(model, specs =  ~ r_condition * variable, data = lm_in)
    
     results = as.data.table(contrast(est_marginal_means, 
                     method = contrast_matrix, 
                     adjust = "dunnettx"))[,eg_modified_sequence := i]
     
     results[,method := "ML"]      
     },
     error = function(e){
       
       results = error_result[,eg_modified_sequence := i]
       
       results[,method := "none"]
       }
   )
  
}
   
toc()

stopCluster(cl)

# Correct for multiple testing using Benjamini-Hochberg

adjusted_abundance_differences = gls_results %>%
  group_by(contrast) %>%
  mutate(adj_pval = p.adjust(p.value, method = "BH"))


fwrite(adjusted_abundance_differences, file = paste0("./Temporal_LiP/GB02_Preprocessed_data/",Run,"_",Experiment_Name,"_GLS_AdjustedAbundance.csv"))


```



