---
title: "GB_TempLiP_Preprocessing"
author: "Aaron Fehr"
date: "2023-06-27"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

This script takes Spectronaut 17 output files for the LiP and tryptic fraction preprocesses the data. It further calculates differential abundance changes with t-tests for the LiP and TrP data. Also, the Adjusted difference is calculated the "MSstats-way", adjusting the fold-changes, propagating the standard error and approximating the degrees of freedom using the Satterthwaite equation.

**Lip data:**

1.  Precursors are filtered based on minimal intensity, q-value and decoy
2.  Calculation of log2-ms2raw-intensities and median normalisation over the whole dataset
3.  Filtering for proteotypicity and calculation of peptide environment (tryptic, semi, coverage ..)
4.  Annotation of "missingness" for precursors based on time-point 0 -\> imputation would be performed here on precursor level
5.  Summing up of precursor intensities to peptide intensities for each modified peptide (chemical entity)
6.  Removal of all peptides with less than 3 observations

**Trp data:**

0.  For qc: same as above

1.  Filter Protein groups based on minimal intensity and pg_qvalue

2.  Calculate log2 protein group intensity

3.  Median normalise protein group inensity

**QC-plots:**

Make qc plots for the data (self explanatory)

**Calculate differential abundance:**

0. Using Protti function for LiP and Trp Set.

1. The differential abundance tables are combined and the error propagated. 

2. The difference is adjusted by calculating the Fold-Change ratio of peptide and protein (subtraction due to log-space)

3. The degrees of freedom are calculated using the Satterthwaite equation and the significance assessed with a standard t-test.

4. P-values are adjusted with Benjamini-Hochberg for each group !no correction is performed for the multiple comparisons!

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(protti)
library(ComplexUpset)
library(broom)
library(data.table)
library(vsn)

```
Read in general stuff
```{r}
# Set experiment name:
Experiment_Name = "GB_TempLiP"
Run = format(Sys.time(), "%y%m%d_%H%M")
Run = "Exclusion_15min"

uniprot = read_tsv("Uniprot_human_230420.tsv") 

uniprot = uniprot %>%
  dplyr::mutate(pg_protein_accessions = Entry, Gene = `Gene Names (primary)`, Sequence, Length)

```

LiP Normalization and summarization to Peptide Level
```{r}
# Read in raw data

raw_lip = read_protti("./Temporal_LiP/Temporal_LiP/GB04_rawfiles/20230627_085946_230609_fehra_GB04_LiP_excluded_Report.xls") %>%
  dplyr::select(r_condition,
                r_file_name,
                r_replicate,
                pg_protein_accessions,
                pg_qvalue,
                pg_quantity,
                pep_is_proteotypic,
                pep_nr_of_missed_cleavages,
                pep_stripped_sequence,
                eg_is_decoy,
                eg_modified_sequence,
                eg_apex_rt,
                eg_qvalue,
                fg_ms2raw_quantity,
                fg_charge) %>%
  dplyr::mutate(sample = paste(r_condition, "LiP", r_replicate, sep = "_")) 

# Normalisation

lip_normalised = raw_lip %>%
  dplyr::filter(eg_is_decoy == FALSE) %>%
  dplyr::filter(eg_qvalue <= 0.01) %>%
  dplyr::filter(fg_ms2raw_quantity >= 10) %>%
  dplyr::mutate(eg_prec_id = paste(eg_modified_sequence, fg_charge, sep ="")) %>%
  dplyr::mutate(intensity_log2 = log2(fg_ms2raw_quantity)) %>%
  protti::normalise(sample, intensity_log2, method = "median") %>%
  dplyr::mutate(normalised_intensity = 2^normalised_intensity_log2)


rm(raw_lip)

# Filtering for proteotypicity
# Joining with Uniprot data and calculation of peptide statistics


lip_filtered_uniprot = lip_normalised %>%
  dplyr::filter(pep_is_proteotypic == 1) %>%
  dplyr::left_join(uniprot,
            by = "pg_protein_accessions") %>%
  dplyr::filter(pg_protein_accessions != "Q99550") %>% # some issue with this protein sequence; 
  protti::find_peptide(protein_sequence = Sequence,
               peptide_sequence = pep_stripped_sequence) %>%
  protti::assign_peptide_type(aa_before = aa_before,
               last_aa = last_aa, 
               aa_after = aa_after) %>%
  protti::calculate_sequence_coverage(protein_sequence = Sequence,
                    peptides = pep_stripped_sequence)

peptide_meta_data = lip_filtered_uniprot %>%
  dplyr::select(pg_protein_accessions,
                Gene,
                eg_modified_sequence,
                pep_stripped_sequence,
                Sequence,
                Length,
                start,
                end,
                aa_before,
                last_aa,
                aa_after,
                pep_nr_of_missed_cleavages,
                pep_is_proteotypic) %>%
  unique()


# Annotate missingness based on time point 0

lip_missingness = lip_filtered_uniprot %>%
    protti::assign_missingness(
      sample = sample,
      condition = r_condition,
      grouping = eg_prec_id,
      intensity = normalised_intensity_log2,
      ref_condition = "0_min",
      completeness_MAR = 0.7,
      completeness_MNAR = 0.2,
      retain_columns = c(Gene,
                         pg_protein_accessions, 
                         r_condition,
                         sample,
                         eg_modified_sequence)
    )


lip_na_filtered = lip_missingness %>%
  dplyr::filter(is.na(normalised_intensity_log2) == FALSE) %>%
  unique()



# Summarization of precursor quantities to peptide level


lip_pep = lip_na_filtered  %>%
  dplyr::mutate(missingness = "complete") %>%
  dplyr::group_by(sample, comparison, eg_modified_sequence) %>%
  dplyr::mutate(pep_int = log2(sum(2^normalised_intensity_log2))) %>%
  dplyr::filter(is.na(pep_int) == FALSE) %>%
  dplyr::mutate(pep_imputed = FALSE) %>%
  dplyr::ungroup() %>%
  dplyr::select(Gene,
                pg_protein_accessions, 
                eg_modified_sequence, 
                sample,
                r_condition, 
                comparison, 
                pep_int, 
                pep_imputed, 
                missingness) %>%
  unique()  %>%
  dplyr::group_by(comparison, r_condition, eg_modified_sequence) %>%
  dplyr::mutate(pep_n_obs = n()) %>%
  dplyr::ungroup() %>%
  dplyr::filter(pep_n_obs >= 3) 


fwrite(lip_pep, file = paste0("./Temporal_LiP/Temporal_LiP/GB04_Preprocessed_data/",Run,"_",Experiment_Name,"_LiP_Summarized_Peptides.csv"))
```
QC of LiP data
```{r}
# Quality Control
# Run Intensities

protti::qc_intensity_distribution(data = lip_normalised,
                          sample = sample,
                          grouping = eg_prec_id,
                          intensity_log2 = intensity_log2,
                          plot_style = "boxplot") +
  labs(title = "Log2 of raw precursor intensity")



protti::qc_median_intensities(data = lip_normalised,
                      sample = sample,
                      grouping = eg_prec_id,
                      intensity = intensity_log2) +
  labs(title = "Log2 of raw precursor intensity")



protti::qc_intensity_distribution(data = lip_normalised,
                          sample = sample,
                          grouping = eg_prec_id,
                          intensity_log2 = normalised_intensity_log2,
                          plot_style = "boxplot") +
  labs(title = "Log2 normalised precursor intensity")

# CV

protti::qc_cvs(lip_normalised,
       grouping = eg_prec_id,
       condition = r_condition,
       intensity = fg_ms2raw_quantity,
       plot = TRUE,
       plot_style = "violin")+
  labs(title = "CV of raw precursor intensity")

protti::qc_cvs(lip_normalised,
       grouping = eg_prec_id,
       condition = r_condition,
       intensity = fg_ms2raw_quantity,
       plot = F)

protti::qc_cvs(lip_normalised,
       grouping = eg_prec_id,
       condition = r_condition,
       intensity = normalised_intensity,
       plot = TRUE,
       plot_style = "violin")  +
  labs(title = "CV of normalised intensity")

protti::qc_cvs(lip_normalised,
       grouping = eg_prec_id,
       condition = r_condition,
       intensity = normalised_intensity,
       plot = F)


# Protein IDs

protti::qc_ids(data = lip_filtered_uniprot,
       sample = sample,
       grouping = pg_protein_accessions,
       intensity = normalised_intensity,
       condition = r_condition, 
       title = "Protein group identifications",
       plot = TRUE)

protti::qc_ids(data = lip_filtered_uniprot,
       sample = sample,
       grouping = eg_modified_sequence,
       intensity = normalised_intensity,
       condition = r_condition, 
       title = "Mod peptide identifications",
       plot = TRUE)

# Peptide type intensity

protti::qc_peptide_type(data = lip_filtered_uniprot,
                sample = sample, 
                peptide = eg_prec_id, 
                pep_type = pep_type, 
                method = "intensity", 
                intensity = fg_ms2raw_quantity, 
                plot = TRUE, 
                interactive = FALSE) +
  labs(title = "Pecursor type intensity")


# Peptide type count

protti::qc_peptide_type(data = lip_filtered_uniprot,
                sample = sample, 
                peptide = eg_prec_id, 
                pep_type = pep_type, 
                method = "count", 
                plot = TRUE, 
                interactive = FALSE) +
  labs(title = "Precursor type count")

# Charge states

protti::qc_charge_states(data = lip_filtered_uniprot, 
                 sample = sample, 
                 grouping = eg_prec_id, 
                 charge_states = fg_charge, 
                 method = "intensity",
                 intensity = fg_ms2raw_quantity, 
                 plot = TRUE) +
  labs(title = "Precursor raw charge state intensity") 




#Missed cleavages

protti::qc_missed_cleavages(data = lip_normalised, 
                    sample = sample, 
                    grouping = eg_prec_id, 
                    missed_cleavages = pep_nr_of_missed_cleavages, 
                    method = "intensity",
                    intensity = fg_ms2raw_quantity, 
                    plot = TRUE) +
  labs(title = "Precursor missed cleavages raw intensity")


# Sequence coverage

protti::qc_sequence_coverage(data = lip_filtered_uniprot,
                     protein_identifier = pg_protein_accessions,
                     coverage = coverage) +
  labs(title = "Protein coverage after filtering")


# Data completeness

protti::qc_data_completeness(data = lip_normalised,
                     sample = sample,
                     grouping = eg_prec_id,
                     intensity = fg_ms2raw_quantity,
                     plot = TRUE) +
  labs(title = "Precursor completeness before filtering")

protti::qc_data_completeness(data = lip_filtered_uniprot,
                     sample = sample,
                     grouping = eg_prec_id,
                     intensity = fg_ms2raw_quantity,
                     plot = TRUE) +
  labs(title = "Precursor completeness after filtering")


# Log2 intensity distribution

protti::qc_intensity_distribution(data = lip_normalised,
                          grouping = eg_prec_id,
                          intensity_log2 = intensity_log2,
                          plot_style = "histogram")  +
  labs(title = "Distribution of log2 raw intensity")


protti::qc_intensity_distribution(data = lip_normalised,
                          grouping = eg_prec_id,
                          intensity_log2 = normalised_intensity_log2,
                          plot_style = "histogram") +
  labs(title = "Distribution of log2 raw intensity")

# PCA

protti::qc_pca(data = lip_normalised,
       sample = sample,
       grouping = eg_prec_id,
       intensity = fg_ms2raw_quantity,
       condition = r_condition,
       digestion = "NULL",
       plot_style = "scree"
) +
labs(title = "PCA plot of raw precursor intensities")

protti::qc_pca(data = lip_normalised,
       sample = sample,
       grouping = eg_prec_id,
       intensity = fg_ms2raw_quantity,
       condition = r_condition,
       components = c("PC1", "PC2"), 
       plot_style = "pca"
) +
labs(title = "PCA plot of raw precursor intensities")


protti::qc_pca(data = lip_normalised,
       sample = sample,
       grouping = eg_prec_id,
       intensity = normalised_intensity_log2,
       condition = r_condition,
       digestion = "NULL",
       plot_style = "scree"
) +
  labs(title = "Scree plot of normalised log2 precursor intensities")

protti::qc_pca(data = lip_normalised,
       sample = sample,
       grouping = eg_prec_id,
       intensity = normalised_intensity_log2,
       condition = r_condition,
       components = c("PC1", "PC2"), 
       plot_style = "pca"
)  +
labs(title = "PCA plot of  normalised log2 precursor  intensities")




# Ranked intensities

protti::qc_ranked_intensities(
  data = lip_normalised,
  sample = sample,
  grouping = eg_prec_id,
  intensity_log2 = normalised_intensity_log2,
  plot = TRUE,
) +
  labs(title = "Ranked normalised precursor intensities")

# Correlation

protti::qc_sample_correlation(data = lip_normalised,
                      sample = sample,
                      grouping = eg_prec_id,
                      intensity_log2 = normalised_intensity_log2,
                      condition = r_condition)




#Number peptides in all conditions:


lip_pep_per_time = lip_pep %>%
  dplyr::select(r_condition, eg_modified_sequence) %>%
  unique() %>%
  group_by(eg_modified_sequence) %>%
  mutate(count = n()) %>%
  ungroup()

lip_pep_per_time %>%
  dplyr::select(count, eg_modified_sequence) %>%
  unique() %>%
  dplyr::select(-eg_modified_sequence) %>%
  group_by(count) %>%
  mutate(n = n()) %>%
  unique()


lip_pep_per_time %>%
  ggplot(aes(count)) +
  geom_histogram(bins = 12)

# rm(lip_normalised)
# rm(lip_na_filtered)
# rm(lip_filtered_uniprot)
# rm(lip_missingness)
# 
# gc()
```

Trp fraction Normalization and Summarization
```{r}
raw_trp = read_protti("./Temporal_LiP/Temporal_LiP/GB04_rawfiles/20230627_090111_230623_fehra_GB04_Trp_Report.xls") %>%
  dplyr::mutate(sample = paste(r_condition, "Trp", r_replicate, sep = "_")) %>%
  dplyr::select(r_condition,
                sample,
                pg_protein_accessions,
                pg_qvalue,
                pg_quantity,
                pep_is_proteotypic,
                pep_nr_of_missed_cleavages,
                pep_stripped_sequence,
                eg_is_decoy,
                eg_modified_sequence,
                eg_qvalue,
                fg_ms2raw_quantity,
                fg_charge) %>%
  dplyr::filter(r_condition != "15_min") 


# Clean tryptic data

# For QC and peptide centric analysis

trp_qc = raw_trp %>%
  dplyr::filter(eg_qvalue <= 0.01) %>%
  dplyr::filter(fg_ms2raw_quantity >= 10) %>%
  dplyr::mutate(eg_prec_id = paste(eg_modified_sequence, fg_charge, sep ="")) %>%
  dplyr::mutate(intensity_log2 = log2(fg_ms2raw_quantity)) %>%
  normalise(sample, intensity_log2, method = "median") %>%
  dplyr::mutate(normalised_intensity = 2^normalised_intensity_log2) %>%
  dplyr::filter(pep_is_proteotypic == TRUE) %>%
  dplyr::left_join(uniprot, by = "pg_protein_accessions") %>%
  protti::find_peptide(protein_sequence = Sequence,
               peptide_sequence = pep_stripped_sequence) %>%
  protti::assign_peptide_type(aa_before = aa_before,
               last_aa = last_aa, 
               aa_after = aa_after)

# Filter & Normalise data

trp_filtered = raw_trp %>%
  dplyr::select(sample, r_condition, pg_protein_accessions, pg_quantity, pg_qvalue) %>%
  dplyr::filter(pg_qvalue <= 0.01) %>%
  dplyr::mutate(pg_log2_intensity = log2(pg_quantity)) %>%
  protti::normalise(sample, pg_log2_intensity, method = "median") %>%
  unique()

# Assign missingness 

trp_missingness =  trp_filtered %>%
    protti::assign_missingness(
      sample = sample,
      condition = r_condition,
      grouping = pg_protein_accessions,
      intensity = normalised_intensity_log2,
      ref_condition = "0_min",
      completeness_MAR = 0.7,
      completeness_MNAR = 0.25,
      retain_columns = c(pg_protein_accessions,
                         pg_log2_intensity,
                         r_condition)
      )

# Summarize data

trp_na_filtered = trp_missingness %>%
  dplyr::mutate(pg_protein_accessions = str_split(pg_protein_accessions, ";")) %>%
  unnest(pg_protein_accessions) %>%
  dplyr::filter(is.na(normalised_intensity_log2) == FALSE) %>%
  dplyr::filter(is.na(missingness) == FALSE) %>%
  dplyr::group_by(r_condition, comparison, pg_protein_accessions) %>%
  dplyr::mutate(n_prot = n()) %>%
  dplyr::filter(n_prot >= 3) %>%
  dplyr::ungroup() %>%
  dplyr::left_join(uniprot, by  = "pg_protein_accessions")



fwrite(trp_na_filtered, file = paste0("./Temporal_LiP/Temporal_LiP/GB04_Preprocessed_data/",Run,"_",Experiment_Name,"_Trp_Summarized_Proteins.csv"))

```

QC of Trp Data
```{r}
# Quality Control

# Run Intensities

protti::qc_intensity_distribution(data = trp_qc,
                          sample = sample,
                          grouping = eg_prec_id,
                          intensity_log2 = intensity_log2,
                          plot_style = "boxplot") +
  labs(title = "Log2 of raw precursor intensity")


protti::qc_median_intensities(data = trp_qc,
                      sample = sample,
                      grouping = eg_prec_id,
                      intensity = intensity_log2) +
  labs(title = "Log2 of raw precursor intensity")



# CV

protti::qc_cvs(trp_filtered,
       grouping = pg_protein_accessions,
       condition = r_condition,
       intensity = pg_quantity,
       plot = TRUE,
       plot_style = "violin")+
  labs(title = "CV of protein intensity")


protti::qc_cvs(trp_filtered,
       grouping = pg_protein_accessions,
       condition = r_condition,
       intensity = pg_quantity,
       plot = FALSE)


# Protein IDs

protti::qc_ids(data = trp_filtered,
       sample = sample,
       grouping = pg_protein_accessions,
       intensity = pg_log2_intensity,
       condition = r_condition, 
       title = "Protein identifications per sample",
       plot = TRUE)



# Peptide type intensity

protti::qc_peptide_type(data = trp_qc,
                sample = sample, 
                peptide = eg_prec_id, 
                pep_type = pep_type, 
                method = "intensity", 
                intensity = fg_ms2raw_quantity, 
                plot = TRUE, 
                interactive = FALSE) +
  labs(title = "Pecursor type intensity")


# Peptide type count

protti::qc_peptide_type(data = trp_qc,
                sample = sample, 
                peptide = eg_prec_id, 
                pep_type = pep_type,
                intensity = fg_ms2raw_quantity,
                method = "count", 
                plot = TRUE, 
                interactive = FALSE)+
  labs(title = "Precursor type count")

# Charge states

protti::qc_charge_states(data = trp_qc, 
                 sample = sample, 
                 grouping = eg_prec_id, 
                 charge_states = fg_charge, 
                 method = "intensity",
                 intensity = fg_ms2raw_quantity, 
                 plot = TRUE)+
  labs(title = "Precursor raw charge state intensity")


#Missed cleavages

protti::qc_missed_cleavages(data = trp_qc, 
                    sample = sample, 
                    grouping = eg_prec_id, 
                    missed_cleavages = pep_nr_of_missed_cleavages, 
                    method = "intensity",
                    intensity = fg_ms2raw_quantity, 
                    plot = TRUE)+
  labs(title = "Precursor missed cleavages raw intensity")


# Peak width

# Data completeness

protti::qc_data_completeness(data = trp_qc,
                     sample = sample,
                     grouping = eg_prec_id,
                     intensity = fg_ms2raw_quantity,
                     plot = TRUE) +
  labs(title = "Precursor completeness before filtering")

protti::qc_data_completeness(data = trp_na_filtered,
                     sample = sample,
                     grouping = pg_protein_accessions,
                     intensity = normalised_intensity_log2,
                     plot = TRUE) +
  labs(title = "Protein completeness after filtering")

# Log2 intensity distribution


protti::qc_intensity_distribution(data = trp_filtered,
                          grouping = pg_protein_accessions,
                          intensity_log2 = pg_log2_intensity,
                          plot_style = "histogram") +
  labs(title = "Distribution of log2 spectronaut protein intensity")

protti::qc_intensity_distribution(data = trp_filtered,
                          grouping = pg_protein_accessions,
                          intensity_log2 = normalised_intensity_log2,
                          plot_style = "histogram")+
  labs(title = "Distribution of log2 normalised protein intensity")
# PCA

# on ms2 raw precursor level
protti::qc_pca(data = trp_qc,
       sample = sample,
       grouping = eg_prec_id,
       intensity = intensity_log2,
       condition = r_condition,
       digestion = "NULL",
       plot_style = "scree"
)+
labs(title = "Scree plot of raw precursor intensities")


protti::qc_pca(data = trp_qc,
       sample = sample,
       grouping = eg_prec_id,
       intensity = intensity_log2,
       condition = r_condition,
       components = c("PC1", "PC2"), 
       plot_style = "pca"
)+
labs(title = "PCA plot of raw precursor intensities")



# PCA on protein group level

protti::qc_pca(data = trp_na_filtered,
       sample = sample,
       grouping = pg_protein_accessions,
       intensity = normalised_intensity_log2 ,
       condition = r_condition,
       digestion = "NULL",
       plot_style = "scree"
)+
  labs(title = "Scree plot of normalised log2 protein intensities")


protti::qc_pca(data = trp_na_filtered,
       sample = sample,
       grouping = pg_protein_accessions,
       intensity = normalised_intensity_log2,
       condition = r_condition,
       components = c("PC1", "PC2"), 
       plot_style = "pca"
)+
  labs(title = "PCA plot of normalised log2 protein intensities")




# Ranked intensities

protti::qc_ranked_intensities(
  data = trp_filtered,
  sample = sample,
  grouping = pg_protein_accessions,
  intensity_log2 = pg_log2_intensity,
  plot = TRUE,
) +
labs(title = "Ranked normalised precursor intensities")

# Correlation


protti::qc_sample_correlation(data = trp_filtered,
                      sample = sample,
                      grouping = pg_protein_accessions,
                      intensity_log2 = normalised_intensity_log2 ,
                      condition = r_condition)
```


Calculation of differential abundances and correction for protein abundance changes
```{r}

diff_abundance_lip  = lip_pep %>%
    protti::calculate_diff_abundance(
      sample = sample,
      condition = r_condition,
      grouping = eg_modified_sequence,
      intensity_log2 = pep_int,
      missingness = missingness,
      comparison = comparison,
      method = "t-test",
      retain_columns = c(Gene,
                         pg_protein_accessions)
  ) %>%
  dplyr::filter(is.na(std_error) == FALSE) %>%
  mutate(time = gsub("_min_vs_0_min","", comparison))


diff_abundance_trp = trp_na_filtered %>%
    protti::calculate_diff_abundance(
      sample = sample,
      condition = r_condition,
      grouping = pg_protein_accessions,
      intensity_log2 = normalised_intensity_log2,
      missingness = missingness,
      comparison = comparison,
      method = "t-test",
      retain_columns = c(Gene)
  ) %>%
  dplyr::filter(is.na(std_error) == FALSE) %>%
  mutate(time = gsub("_min_vs_0_min","", comparison))


# Adjustment according to MSstats PTM

adj_abundance = diff_abundance_lip %>%
  dplyr::select(-pval, -adj_pval) %>%
  unique() %>%
  dplyr::inner_join(diff_abundance_trp %>%
              dplyr::select(pg_protein_accessions, time, std_error, diff, n_obs) %>%
              unique(),
            by = c("pg_protein_accessions", "time"), suffix = c("_pep","_prot")) %>%
  dplyr::mutate(adj_diff = diff_pep-diff_prot) %>%
  dplyr::mutate(adj_std_error = sqrt(std_error_pep**2 + std_error_prot**2)) %>%
  dplyr::mutate(numer = (std_error_pep**2 + std_error_prot**2)**2) %>%
  dplyr::mutate(denom = (std_error_pep**4/(n_obs_pep-2) + std_error_prot**4/(n_obs_prot-2))) %>%
  dplyr::mutate(df = numer/denom) %>%
  dplyr::mutate(tval = adj_diff/adj_std_error) %>%
  dplyr::mutate(pval = 2*stats::pt(abs(tval), df, lower.tail = FALSE)) %>%
  dplyr::group_by(time) %>%
  dplyr::mutate(p.adj = p.adjust(pval, method = "BH")) %>%
  dplyr::ungroup()


```

Export of differential abundance tables
```{r}
fwrite(diff_abundance_lip, file = paste0("./Temporal_LiP/GB04_Preprocessed_data/",Run,"_",Experiment_Name,"_LiP_DifferentialAbundance.csv"))
fwrite(diff_abundance_trp, file = paste0("./Temporal_LiP/GB04_Preprocessed_data/",Run,"_",Experiment_Name,"_Trp_DifferentialAbundance.csv"))
fwrite(adj_abundance, file = paste0("./Temporal_LiP/GB04_Preprocessed_data/",Run,"_",Experiment_Name,"_MSstatsAdj_DifferentialAbundance.csv"))
fwrite(peptide_meta_data, file = paste0("./Temporal_LiP/GB04_Preprocessed_data/",Run,"_",Experiment_Name,"_LiP_PeptideMetaData.csv"))

```
