---
title: "GB04_Dataanalysis"
author: "Aaron Fehr"
date: "2023-06-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(data.table)
library(protti)
library(ComplexUpset)
library(broom)
library(reshape2)
library(clusterProfiler)
library(factoextra)
library(cluster)
library(RColorBrewer)
library(ggvenn)
library(dtwclust)
library(STRINGdb)
library(factoextra)
library(foreach)
library(doParallel)
library(e1071)
library(dtwclust)


organism = "org.Hs.eg.db"


library(org.Hs.eg.db)

```

Read in preprocessed data

```{r}
sw_adj = fread("./Temporal_LiP/GB04_Preprocessed_data/230627_1830_GB_TempLiP_MSstatsAdj_DifferentialAbundance.csv")

gls_adj_raw = fread("./Temporal_LiP/GB04_Preprocessed_data/230628_0137_GB_TempLiP_GLS_AdjustedAbundance.csv")

pep_metadata = fread("./Temporal_LiP/GB04_Preprocessed_data/230627_1830_GB_TempLiP_LiP_PeptideMetaData.csv")

prot_raw = fread("./Temporal_LiP/GB04_Preprocessed_data/230627_1830_GB_TempLiP_Trp_Summarized_Proteins.csv")

lip_pep = fread("./Temporal_LiP/GB04_Preprocessed_data/230627_1830_GB_TempLiP_LiP_Summarized_Peptides.csv") %>%
  left_join(pep_metadata)

Sohyon_raw = fread("./Temporal_LiP/PublicationData/PROT_ttest_results_summary.txt") 

uniprot = fread("Uniprot_human_230420.tsv")
```

Protein level analysis (investigate if treatment worked)
```{r}
# calculate protein differential abundances 

prot_diff_abundance = prot_raw %>%
  calculate_diff_abundance(
    sample = sample,
    condition = r_condition, 
    grouping = pg_protein_accessions,
    intensity_log2 = pg_log2_intensity,
    missingness = missingness,
    comparison = comparison,
    method = "t-test",
    retain_columns = Gene
  ) %>%
  separate(comparison, into = c("time","trash"), sep = "_") %>%
  mutate(time = paste0(time,"_min"))

#make time data  

prot_time = rbind(
  prot_diff_abundance %>%
    dplyr::select(Gene,
                  pg_protein_accessions,
                  time,
                  diff,
                  adj_pval,
                  std_error),
  prot_diff_abundance %>%
    dplyr::select(Gene,
                  pg_protein_accessions,
                  time,
                  diff,
                  adj_pval,
                  std_error) %>%
    mutate(time = "0_min",
           diff = 0,
           adj_pval = 1) %>%
    unique()) %>%
  group_by(pg_protein_accessions) %>%
  mutate(time_num = as.numeric(gsub("_min","",time))) %>%
  mutate(max_est = max(abs(diff))) %>%
  mutate(min_adj_pval = min(adj_pval)) %>%
  mutate(sig = adj_pval <= 0.05 & abs(diff) >= 1) %>%
  mutate(n_sig = sum(sig)) %>%
  mutate(zscore = scale(diff, center = TRUE, scale = TRUE)) %>%
  arrange(pg_protein_accessions, time_num) %>%
  mutate(adjecent_sig = max(sig) * (max(cumsum(sig * lag(sig, default = 0))) +1)) %>%
  ungroup() %>%
  group_by(pg_protein_accessions, time) %>%
  mutate(n_sig_per_prot = sum(sig)) %>%
  mutate(n_tot = n()) %>%
  mutate(rel_sig_per_prot = n_sig_per_prot/n_tot) %>%
  ungroup()


# Data Sohyon

Sohyon = rbind(
  Sohyon_raw %>%
    dplyr::select(Gene = Protein_name_simplified, diff = Timepoint_3_vs_0_log2FC, adj_pval = Timepoint_3_vs_0_pval_neglog10) %>%
    mutate(time = "360_min", time_num = 180, adj_pval = 10^-adj_pval, Exp = "Sohon 3h"),
  Sohyon_raw %>%
    dplyr::select(Gene = Protein_name_simplified, diff = Timepoint_9_vs_0_log2FC, adj_pval = Timepoint_9_vs_0_pval_neglog10) %>%
    mutate(time = "360_min", time_num = 360, adj_pval = 10^-adj_pval, Exp = "Sohon 9h"))

Sohyon_time = prot_time %>%
  dplyr::filter(adj_pval > 1) %>%
  full_join(Sohyon)
```

```{r}

relevant_proteins_publication = c("JUN","JUNB","JUND","MAFF","EGR1","EGR2","HSPB1")

t = rbind(
  prot_time %>%
    mutate(Exp = "sadf"),
  Sohyon_time) %>%
  mutate(title = "Protein quantities ") %>%
  dplyr::filter(Gene %in% relevant_proteins_publication)

t  %>%
  ggplot(aes(x = time_num, y = diff, color = Exp))+
  theme_bw() +
  theme(strip.background = element_blank()) +  
  geom_ribbon(aes(ymin = diff - std_error, ymax = diff + std_error), alpha = 0.3, color = "grey", fill = "grey") +
  geom_line() +
  geom_point(size = 2) +
  geom_hline(yintercept = 0) +
  labs(y = "Protein log2FC", x = "time") +
  facet_wrap(. ~ Gene)

# 
# 
# plot
# 
# ggsave("./Temporal_LiP/GB04_AnalysisOutput/GB04_plots/Protein_Traces.png",
#        plot,
#        height = 5,
#        width = 5
#        )


```




Data wrangling and make time series data frame
```{r}
gls_adj = gls_adj_raw %>%
  mutate(time = gsub("-0_min","",contrast)) %>%
  left_join(pep_metadata %>%
              dplyr::select(Gene, pg_protein_accessions, eg_modified_sequence) %>%
              unique(),
            by = "eg_modified_sequence")


gls_time = rbind(
  gls_adj %>%
    dplyr::select(Gene,
                  pg_protein_accessions,
                  eg_modified_sequence,
                  time,
                  estimate,
                  adj_pval),
  gls_adj %>%
    dplyr::select(Gene,
                  pg_protein_accessions,
                  eg_modified_sequence,
                  time,
                  estimate,
                  adj_pval) %>%
    mutate(time = "0_min",
           estimate = 0,
           adj_pval = 1) %>%
    unique()) %>%
  group_by(eg_modified_sequence) %>%
  mutate(mean_est = mean(estimate)) %>%
  mutate(estimate = case_when(
    mean_est < 0 ~ - estimate,
    mean_est >= 0 ~ estimate
  )) %>%
  dplyr::select(-mean_est) %>%  
  mutate(time_num = as.numeric(gsub("_min","",time))) %>%
  mutate(max_est = max(abs(estimate))) %>%
  mutate(min_adj_pval = min(adj_pval)) %>%
  mutate(sig = adj_pval <= 0.05 & abs(estimate) >= 1) %>%
  mutate(n_sig = sum(sig)) %>%
  mutate(zscore = scale(estimate, center = TRUE, scale = TRUE)) %>%
  mutate(max_min_score = (estimate - min(estimate))/(max(estimate)-min(estimate))) %>%
  arrange(eg_modified_sequence, time_num) %>%
  mutate(adjecent_sig = max(sig) * (max(cumsum(sig * lag(sig, default = 0))) +1)) %>%
  ungroup() %>%
  group_by(pg_protein_accessions, time) %>%
  mutate(n_sig_per_prot = sum(sig)) %>%
  mutate(n_tot = n()) %>%
  mutate(rel_sig_per_prot = n_sig_per_prot/n_tot) %>%
  ungroup()



# make wider data frame and filter for significance and >= 2 peptides/protein

gls_time_wide = gls_time %>%
  dplyr::filter(n_tot > 1) %>%
  dplyr::filter(n_sig > 1) %>%
  pivot_wider(id_cols = c("Gene","pg_protein_accessions", "eg_modified_sequence","adjecent_sig"), values_from = c("max_min_score"), names_from = "time") 

```

Data wrangling and make time series data frame
```{r}
gls_adj = gls_adj_raw %>%
  mutate(time = gsub("-0_min","",contrast)) %>%
  left_join(pep_metadata %>%
              dplyr::select(Gene, pg_protein_accessions, eg_modified_sequence) %>%
              unique(),
            by = "eg_modified_sequence")


gls_time = rbind(
  gls_adj %>%
    dplyr::select(Gene,
                  pg_protein_accessions,
                  eg_modified_sequence,
                  time,
                  estimate,
                  adj_pval),
  gls_adj %>%
    dplyr::select(Gene,
                  pg_protein_accessions,
                  eg_modified_sequence,
                  time,
                  estimate,
                  adj_pval) %>%
    mutate(time = "0_min",
           estimate = 0,
           adj_pval = 1) %>%
    unique()) %>%
  group_by(eg_modified_sequence) %>%
  mutate(mean_est = mean(estimate)) %>%
  mutate(estimate = case_when(
    mean_est < 0 ~ - estimate,
    mean_est >= 0 ~ estimate
  )) %>%
  dplyr::select(-mean_est) %>%  
  mutate(time_num = as.numeric(gsub("_min","",time))) %>%
  mutate(max_est = max(abs(estimate))) %>%
  mutate(min_adj_pval = min(adj_pval)) %>%
  mutate(sig = adj_pval <= 0.05 & abs(estimate) >= 1) %>%
  mutate(n_sig = sum(sig)) %>%
  mutate(zscore = scale(estimate, center = TRUE, scale = TRUE)) %>%
  mutate(max_min_score = (estimate - min(estimate))/(max(estimate)-min(estimate))) %>%
  arrange(eg_modified_sequence, time_num) %>%
  mutate(adjecent_sig = max(sig) * (max(cumsum(sig * lag(sig, default = 0))) +1)) %>%
  ungroup() %>%
  group_by(pg_protein_accessions, time) %>%
  mutate(n_sig_per_prot = sum(sig)) %>%
  mutate(n_tot = n()) %>%
  mutate(rel_sig_per_prot = n_sig_per_prot/n_tot) %>%
  ungroup()



# make wider data frame and filter for significance and >= 2 peptides/protein

gls_time_wide = gls_time %>%
  dplyr::filter(n_tot > 1) %>%
  dplyr::filter(n_sig > 1) %>%
  pivot_wider(id_cols = c("Gene","pg_protein_accessions", "eg_modified_sequence","adjecent_sig"), values_from = c("max_min_score"), names_from = "time") 

```

Plot of number of changes
```{r}
# Changes per time point and protein 

relative_changes_plot = gls_time %>%
  dplyr::filter(time_num != 0) %>%
  dplyr::filter(n_sig_per_prot > 0) %>%
  dplyr::select(time_num, rel_sig_per_prot) %>%
  unique() %>%
  ggplot(aes(rel_sig_per_prot)) +
  theme_classic() +
  scale_fill_brewer(palette = "BuPu") +
  geom_histogram(color = "black", bins = 25, fill = "lightgrey") +
  labs(title = " ", x = "Relative LiP changes per protein", y = "Number of peptides per bin") +
  facet_wrap(. ~ as.factor(time_num))


relative_changes_plot



ggsave("./Temporal_LiP/GB04_AnalysisOutput/GB04_plots/Relative_Changes.png",
       relative_changes_plot,
       height = 4,
       width = 7)


```

Hierarchical Clustering

```{r}
set.seed(1234)
# Parameters to test:

k_clusters = 30

# Make cluster data
cluster_data_lip = gls_time_wide[5:ncol(gls_time_wide)]

# calculate distance matrix and clusters

dist = dist(cluster_data_lip) 

hc_lip = hclust(dist, method = "average")

clusters = cutree(hc_lip, h = 0.6)

# Combine with original data

lip_hc_clustered = cbind(gls_time_wide, clusters) %>%
  as.data.frame() %>%
  dplyr::select(eg_modified_sequence, clusters) %>%
  left_join(gls_time) %>%
  group_by(clusters, time) %>%
  mutate(obs_per_cluster = n()) %>%
  mutate(est_centroid = mean(estimate)) %>%
  mutate(zscore_centroid = mean(zscore)) %>%
  mutate(maxmin_centroid = mean(max_min_score)) %>%
  ungroup()

# Plotting of Dendrogram

plot(hc_lip, main = "Hierarchical clustering of LiP data:",xlab = "", ylab = "", pch = clusters, labels = F)
rect.hclust(hc_lip, k = length(unique(clusters)), cluster = clusters)

svg("./Temporal_LiP/GB04_AnalysisOutput/GB04_plots/Dendrogram.svg")

# Code of the plot
plot(hc_lip, main = "Hierarchical clustering of LiP data:",xlab = "", ylab = "", pch = clusters, labels = F)
rect.hclust(hc_lip, k = length(unique(clusters)), cluster = clusters)

dev.off() 

# PCA + Clusters

fviz_cluster(list(data = cluster_data_lip, cluster = clusters))

```




Peptide trace plots: 
```{r}
# All time series:

plot = rbind(lip_hc_clustered %>%
  dplyr::select(time_num, eg_modified_sequence, clusters, FC = max_min_score, Centroid = maxmin_centroid) %>%
  mutate(Norm = "Max-Min-FC"),
  lip_hc_clustered %>%
  dplyr::select(time_num, eg_modified_sequence, clusters, FC = estimate, Centroid = est_centroid) %>%
  mutate(Norm = "Log2-FC")) %>%
  mutate(clusters = paste0("Cluster ",clusters)) %>%
  ggplot(aes(x = time_num, y = FC, group = eg_modified_sequence)) +
  geom_line(alpha = 0.2)+
  geom_line(aes(x = time_num, y = Centroid, color = "red")) +
  geom_point(aes(x = time_num, y = Centroid, color = "red")) +
  theme_bw()+
  theme(strip.background = element_blank()) +
  theme(axis.text.x = element_text(hjust = 1, angle = 45)) +
  facet_grid(Norm ~ clusters,  scales = "free_y")+
  labs(title = " ", x = "", y = "")+
  guides(color="none")

plot


ggsave("./Temporal_LiP/GB04_AnalysisOutput/GB04_plots/All_ts_cluster_plot.png",
       plot,
       height = 3,
       width = 10)

# Selected clusters (over 40 peptides)


plot = rbind(lip_hc_clustered %>%
  dplyr::filter(obs_per_cluster >= 40) %>%
  dplyr::select(time_num, eg_modified_sequence, clusters, FC = max_min_score, Centroid = maxmin_centroid) %>%
  mutate(Norm = "Max-Min-FC"),
  lip_hc_clustered %>%
  dplyr::filter(obs_per_cluster >= 40) %>%
  dplyr::select(time_num, eg_modified_sequence, clusters, FC = estimate, Centroid = est_centroid) %>%
  mutate(Norm = "Log2-FC")) %>%
  mutate(clusters = paste0("Cluster ",clusters)) %>%
  ggplot(aes(x = time_num, y = FC, group = eg_modified_sequence)) +
  geom_line(alpha = 0.2)+
  geom_line(aes(x = time_num, y = Centroid, color = "red")) +
  geom_point(aes(x = time_num, y = Centroid, color = "red")) +
  theme_bw()+
  theme(strip.background = element_blank()) +
  facet_grid(Norm ~ clusters,  scales = "free_y")+
  labs(title = " ", x = "", y = "")+
  guides(color="none")
  
plot

ggsave("./Temporal_LiP/GB04_AnalysisOutput/GB04_plots/Selected_ts_cluster_plot.png",
       plot,
       height = 3,
       width = 10)


```



Call proteins based on cluster abundance

```{r}
# Call proteins based on cluster annotation -> majority vote
# If same number of peptides from multiple clusters -> in multiple clusters

hc_call = lip_hc_clustered  %>%
  group_by(clusters, time) %>%
  unique() %>%
  dplyr::select(Gene, eg_modified_sequence, pg_protein_accessions, clusters) %>%
  unique() %>%
  group_by(pg_protein_accessions) %>%
  mutate(n_pep = n()/5) %>%
  group_by(pg_protein_accessions, clusters) %>%
  mutate(n_per_cluster = n()/5) %>%
  group_by(pg_protein_accessions) %>%
  mutate(rel = n_per_cluster/n_pep) %>%
  mutate(max_rel = max(rel)) %>%
  ungroup() %>%
  dplyr::filter(rel == max_rel) %>% 
  dplyr::select(Gene, pg_protein_accessions, clusters, max_rel, n_pep) %>%
  unique() %>%
  group_by(clusters) %>%
  mutate(prot_per_cluster = n()) %>%
  ungroup()

hc_call %>%
  group_by(Gene) %>%
  mutate(N = n()) %>%
  ungroup() %>%
  dplyr::select(N) %>%
  group_by(N) %>%
  mutate(Number_n = n()) %>%
  unique()

lip_hc_clustered %>%
  dplyr::select(clusters, Gene) %>%
  unique() %>%
  group_by(Gene) %>%
  mutate(N = n()) %>%
  ungroup() %>%
  dplyr::select(N) %>%
  group_by(N) %>%
  mutate(Number_n = n()) %>%
  unique()

```


Plot with significant pep/prot per time point and features per cluster
```{r}
# Significant changes per time point:

sig_per_time = rbind(
  gls_time %>%
    dplyr::select(pg_protein_accessions, x_value = time_num, sig) %>%
    group_by(x_value, pg_protein_accessions) %>%
    mutate(sig_prot = sum(sig) > 0) %>%
    dplyr::select(sig_prot) %>%
    unique()  %>%
    group_by(x_value) %>%
    mutate(value = sum(sig_prot)/n()*100) %>%
    dplyr::select(value) %>%
    mutate(entity = "Protein") %>%
    unique(),
  gls_time %>%
    dplyr::select(eg_modified_sequence, x_value = time_num, sig) %>%
    group_by(x_value) %>%
    mutate(value = sum(sig)/n()*100) %>%
    dplyr::select(value) %>%
    unique()  %>%
    mutate(entity = "Peptide")) %>%
  dplyr::filter(x_value != 0) %>%
  arrange(x_value) %>%
  ungroup() %>%
  mutate(order = row_number()) %>%
  mutate(x_value = as.character(x_value)) %>%
  mutate(facet = "% Significant/time point")


plot = sig_per_time %>%
  mutate(x_value = fct_reorder(x_value, order)) %>%
  ggplot(aes(x = x_value, y = value, fill = entity)) +
  geom_col(position = position_dodge(), color = "black")+
  theme_bw()+ 
  theme(legend.position = "left",
        legend.key.size = unit(0.4, "cm"),
        legend.margin = margin(r=- 0.6, unit = "cm")) + 
  theme(panel.grid = element_blank()) +
  theme(strip.background = element_blank()) +
  scale_fill_brewer(palette = "BuPu") +
  labs(title = " ",x = "", y = "", fill = "")+
  facet_wrap(. ~ facet, scales = "free")
  
plot

ggsave(paste0("./Temporal_LiP/GB04_AnalysisOutput/GB04_plots/Relative_Sig_per_timepoint.png"),
      plot,
      height = 3,
      width = 5)


#Plot Features per cluster

n_per_cluster = rbind(
  lip_hc_clustered %>%
    dplyr::select(eg_modified_sequence, x_value = clusters) %>%
    unique() %>%
    group_by(x_value) %>%
    mutate(value = n()) %>%
    dplyr::select(value) %>%
    unique() %>%
    mutate(entity = "Peptide") %>%
    mutate(x_value = case_when(
       value < 40 ~ "other",
       TRUE ~ as.factor(x_value)
    )) %>%
    mutate(value = sum(value)) %>%
    unique(),  
  lip_hc_clustered %>%
    dplyr::select(pg_protein_accessions, x_value = clusters) %>%
    unique() %>%
    group_by(x_value) %>%
    mutate(value = n()) %>%
    dplyr::select(value) %>%
    unique() %>%
    mutate(x_value = case_when(
       value < 30 ~ "other",
       TRUE ~ as.factor(x_value))
       ) %>%
    mutate(value = sum(value)) %>%
    unique() %>%
    mutate(entity = "Protein")) %>%
  ungroup() %>%
  arrange(as.numeric(x_value)) %>%
  mutate(order = row_number()) %>%
  mutate(facet = "Features per cluster")



plot = n_per_cluster %>%
  mutate(x_value = fct_reorder(as.factor(x_value), order)) %>%
  ggplot(aes(x = x_value, y = value, fill = entity)) +
  geom_col(position = position_dodge(), color = "black")+
  theme_bw()+ 
  theme(legend.position = "left",
        legend.key.size = unit(0.4, "cm")) + 
  theme(panel.grid = element_blank()) +
  theme(strip.background = element_blank()) +
  scale_fill_brewer(palette = "BuPu") +
  labs(title = " ",x = "", y = "# features", fill = "")+
  facet_wrap(. ~ facet, scales = "free")
  
plot

ggsave(paste0("./Temporal_LiP/GB04_AnalysisOutput/GB04_plots/Features_per_cluster.png"),
      plot,
      height = 3,
      width = 4.5)



# Combined:


plot = rbind(sig_per_time, n_per_cluster) %>%
  mutate(x_value = fct_reorder(x_value, order)) %>%
  ggplot(aes(x = x_value, y = value, fill = entity)) +
  geom_col(position = position_dodge(), color = "black")+
  theme_bw()+ 
  theme(legend.position = "left",
        legend.key.size = unit(0.4, "cm"),
        legend.margin = margin(r=- 0.6, unit = "cm")) + 
  theme(panel.grid = element_blank()) +
  theme(strip.background = element_blank()) +
  scale_fill_brewer(palette = "BuPu") +
  labs(title = " ",x = "", y = "", fill = "")+
  facet_wrap(. ~ facet, scales = "free")

plot

ggsave(paste0("./Temporal_LiP/GB04_AnalysisOutput/GB04_plots/Features_per_clusterANDSigPerTP.png"),
      plot,
      height = 3,
      width = 5)


#For dendrogram title:

plot = n_per_cluster %>%
  mutate(facet = "Hierarchical clustering of peptide traces") %>%
  mutate(x_value = "", value = 0) %>%
  ggplot(aes(x = x_value, y = value)) +
  geom_col(position = position_dodge(), color = "black")+
  theme_bw()+ 
  theme(axis.ticks.x = element_blank())+
  scale_y_continuous(limits = c(-0.25,1.5), breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1, 1.2, 1.4)) +
  theme(legend.position = "left",
        legend.key.size = unit(0.4, "cm"),
        legend.margin = margin(r=- 0.6, unit = "cm")) + 
  theme(panel.grid = element_blank()) +
  theme(strip.background = element_blank()) +
  scale_fill_brewer(palette = "BuPu") +
  labs(title = " ",x = "", y = "", fill = "")+
  facet_wrap(. ~ facet, scales = "free")

ggsave(paste0("./Temporal_LiP/GB04_AnalysisOutput/GB04_plots/DendroTitle.jpeg"),
      plot,
      height = 3,
      width = 5)

```


Nice QC-plot for supplementary:

```{r}
# Coefficients of variation: 
plot = lip_pep %>%
  mutate(sample = gsub("min_LiP_","",sample)) %>%
  mutate(intensity = 2^pep_int) %>%
  qc_cvs(
    grouping = eg_modified_sequence,
    condition = r_condition,
    intensity = intensity,
    plot_style = "violin")  +
  theme(legend.position = "none") +
  labs(title = "Coefficients of variation of mod. peptides")



plot 

ggsave("./Temporal_LiP/GB04_AnalysisOutput/QC_plots/GB04_liP_CVs.png",
       plot,
       height = 3.5,
       width = 10)
 
  
lip_pep %>%
  mutate(sample = gsub("min_LiP_","",sample)) %>%
  mutate(intensity = 2^pep_int) %>%
  qc_cvs(
    grouping = eg_modified_sequence,
    condition = r_condition,
    intensity = intensity,
    plot = F
  )


# Number of peptide identifications:

plot = lip_pep %>%
  mutate(sample = gsub("min_LiP_","",sample)) %>%
  qc_ids(
       sample = sample,
       grouping = eg_modified_sequence,
       intensity = pep_int,
       condition = r_condition,
       plot = T) +
  theme(legend.position = "none") +
  labs(title = "Mod. peptide identifications")

plot 

ggsave("./Temporal_LiP/GB04_AnalysisOutput/QC_plots/GB04_liP_IDs.png",
       plot,
       height = 3.5,
       width = 10)

# Peptide type:

plot = lip_pep %>%
  mutate(sample = gsub("min_LiP_","",sample)) %>%
  assign_peptide_type(aa_before = aa_before,
               last_aa = last_aa, 
               aa_after = aa_after) %>%
  qc_peptide_type(
    sample = sample,
    peptide = eg_modified_sequence,
    pep_type = pep_type,
    method = "intensity",
    intensity = pep_int,
    plot = T
  ) +
  labs(title = "Mod. peptide type intensities")

plot 

ggsave("./Temporal_LiP/GB04_AnalysisOutput/QC_plots/GB04_liP_pep_types.png",
       plot,
       height = 4.68,
       width = 20)

# PCA:

plot = lip_pep %>%
  qc_pca(
    sample = sample,
    grouping = eg_modified_sequence,
    intensity = pep_int,
    condition = r_condition,
    components = c("PC1","PC2"),
    plot_style = "pca"
  )

plot 

ggsave("./Temporal_LiP/GB04_AnalysisOutput/QC_plots/GB04_liP_pca.png",
       plot,
       height = 5,
       width = 10)

# Hierarchical clustering

plot = lip_pep %>%
  mutate(sample = gsub("min_LiP_","",sample)) %>%
  qc_sample_correlation(
    sample = sample,
    grouping = eg_modified_sequence,
    intensity_log2 = pep_int,
    condition = r_condition
    )


plot 

ggsave("./Temporal_LiP/GB04_AnalysisOutput/QC_plots/GB04_liP_heatmap.png",
       plot,
       height = 6,
       width = 10)
```
